---
title: "Cardinal temperatures"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style2.css
    social: menu
editor_options: 
  chunk_output_type: inline
---

# Dashboard

## Inputs {.sidebar data-width="250"}

```{r include=FALSE}
library(tidyverse)
library(janitor)
library(gsheet)
dat <- read_csv("cardinal-temperature.csv")
url <- 'https://docs.google.com/spreadsheets/d/14ssaUpLuVCT53qnQrQHk0gHh2SFn2prUY6Af078P648/edit?usp=sharing'
dat2 <- gsheet2tbl(url)
cardinal <- dat %>% 
  separate(SPECIES_FINAL, c("GENUS", "EPITHET"), " ", remove = F) %>% 
  select(CLASS, SPECIES_FINAL,  PROCESS,CARDINAL, TEMPERATURE, DISEASE, HOST_PLANT, TEMPERATURE_REFERENCE)

cardinal$CARDINAL <- factor(cardinal$CARDINAL, c("min", "opt", "max"))




```

```{r}
library(crosstalk)
sd <- SharedData$new(cardinal)
```

```{r}

filter_checkbox("CLASS", "Class", sd, ~CLASS, inline = F)
filter_checkbox("PROCESS", "Process", sd, ~PROCESS, inline = F)
filter_select("SPECIES_FINAL", "Species", sd, ~SPECIES_FINAL)

```

This interactive dashboard displays the data on the "cardinal temperatures" - minimum (Tmin), optimum (Topt) and maximum (Tmax) temperatures of five life-cycle processes (disease development, fructification, infection , spore germination and sporulation ), as well as growth in culture which were extracted for fungi and oomycete species. The data are available online at: <https://datadryad.org/stash/dataset/doi:10.5061/dryad.tqjq2bvw6>. The publication can be found at: <https://www.nature.com/articles/s41467-020-16778-5>

## Grid view

### Grid view

```{r}
library(plotly)
library(DT)
datatable(sd, 
          extensions = c('Buttons'),
          escape = TRUE, rownames = FALSE,
         class = 'cell-border stripe',
                      options=list(dom = 'Bfrtip',buttons = c( 'excel'),deferRender=TRUE, 
                          scrollY=500, 
                          scroller=TRUE,
                          colReorder = TRUE,
                          pageLength = 100))

```

## Column {.tabset data-width="500"}

### Cardinal by process

```{r}
library(viridis)
sd %>% 
  plot_ly( x = ~ CARDINAL,
          y = ~ TEMPERATURE, color = ~ PROCESS, type = "box") %>% 
  layout(boxmode = "group") %>%
config(displayModeBar = F)
 
```

### Cardinal by class 

```{r}
library(viridis)
sd %>% 
  plot_ly( x = ~ CARDINAL,
          y = ~ TEMPERATURE, color = ~ CLASS, type = "box") %>% 
  layout(boxmode = "group")%>%
config(displayModeBar = F)
 
```


### Temperature by process and class

```{r}
library(viridis)
sd %>% 
  
  plot_ly( x = ~ PROCESS,
          y = ~ TEMPERATURE, color = ~ CLASS, type = "box") %>% 
  layout(boxmode = "group")%>%
config(displayModeBar = F)
 
```

